Groth16 zk-SNARK Proof Verification on Freeton : Three Use Cases

### 2021-07-14 submission/submission.tex
remove old script + changes to submission after call with Fabrice

	\item[Marshalling and memory corruption:] Because of a memory corruption error in the marshalling of the verification key, we were unable to do a full 9 by 9 Sudoku, restricting ourselves to 4 by 4. All our code is generic (it is generated from an OCaml program which takes as a parameter the value $n$ such that the Sudoku is $n^2$ by $n^2$). We were told that after the contest, a more robust marshalling library would be provided. In any case we would be glad to discuss this issue with the Nil foundation team to give users the full Sudoku experience! In the meantime, a 4 by 4 Sudoku is sufficient to get a sense of the dynamics of \zksnark-based Sudoku.

@@

As mentioned in Section \ref{subsec:general_remarks}, we had to restrict ourselves to a 4 by 4 Sudoku grid, even though our code generator is generic in the grid size. This is because the marshalling function on the 9 by 9 code produced a memory corruption error.

@@

\begin{description}
	\item[The cli:] it is a C++ program linked to the Blueprint \zksnarks{} library. It can be used in two different ways:
	\begin{itemize}
		\item To create the original proving and verification keys. This step is independent of any given Sudoku instance and should only be done once.
		\item To generate a proof given an instance and a solution. The instance is given as a text file such as

@@

		Note that if your solution is not correct, this step will fail.
	\end{itemize}
    \item[The Sudoku smart contract:] The main function of this smart contract is
    \begin{lstlisting}[language=Solidity]
    function submit(bytes proof)
        public view returns (bool res, string blob_str)
    \end{lstlisting}
    It will check the input proof against the verification key \lstinline[language=Solidity]|v_key| and the current instance \lstinline[language=Solidity]|m_instance|, both local to the contract. This instance is stored as an array of \lstinline[language=Solidity]|fixed_value|:
    \begin{lstlisting}[language=Solidity]
    struct fixed_value {
      uint8 i;
      uint8 j;
      uint8 value;
    }

@@

\subsection{Code}
\label{subsec:sudoku_code}

TODO: code du sudoku ici

@@

Compared to other approaches, this use can provide several
improvements:
\begin{itemize}
\item The user does not disclose his passphrase. Most other approaches
  (based on hashes for example) give an opportunity for
  man-in-the-middle attacks ;
\item As the user does not disclose his passphrase, the pubkey can be
  replaced several times ;
\item The user does not need to create the new public key ahead of
  time. Instead, he can create it when he has lost the former one,
  decreasing the likelihood of losing the associated secret key also ;
\end{itemize}

>>>>

	\item[Marshalling and memory corruption:] Because of a memory
          corruption error in the marshalling function (in the code
          provided for the contests) of the verification key, we were
          unable to do a full 9 by 9 Sudoku, restricting ourselves to
          4 by 4. All our code is generic (it is generated from an
          OCaml program which takes as a parameter the value $n$ such
          that the Sudoku is $n^2$ by $n^2$). We were told that after
          the contest, a more robust marshalling library would be
          provided. In any case we would be glad to discuss this issue
          with the Nil foundation team to give users the full Sudoku
          experience! In the meantime, a 4 by 4 Sudoku is sufficient
          to get a sense of the dynamics of \zksnark-based Sudoku.

@@

As mentioned in Section \ref{subsec:general_remarks}, we had to
restrict ourselves to a 4 by 4 Sudoku grid, even though our code
generator is generic in the grid size. This is because the marshalling
function (in the codep rovided for the contest) on the 9 by 9 code
produced a memory corruption error.

@@

\begin{description}
\item[The cli:] it is a C++ program linked to the Blueprint \zksnarks{} library. It can be used in two different ways:

  TODO: mettre un exemple
  copier coller la commande

	\begin{itemize}
		\item To create the original proving and verification keys. This step is independent of any given Sudoku instance and should only be done once.
		\item To generate a proof given an instance and a solution. The instance is given as a text file such as

@@

		Note that if your solution is not correct, this step will fail.
	\end{itemize}
    \item[The Sudoku smart contract:] The main function of this smart contract is
    \begin{lstlisting}[language=Solidity]
    function submit(bytes proof)
        public view returns (bool res, string blob_str)
    \end{lstlisting}
    It will check the input proof against the verification key
    \lstinline[language=Solidity]|v_key| and the current instance
    \lstinline[language=Solidity]|m_instance|, which are both local to
    the contract and set in the constructor. This instance is stored
    as an array of \lstinline[language=Solidity]|fixed_value|:
    \begin{lstlisting}[language=Solidity]
    struct fixed_value {
      uint8 i;
      uint8 j;
      uint8 value;
    }

@@

@@

Compared to other approaches, this use can provide several
improvements:
\begin{itemize}
\item The user does not disclose his passphrase. Most other approaches
  (based on hashes for example) give an opportunity for
  man-in-the-middle attacks;
\item As the user does not disclose his passphrase, the pubkey can be
  replaced several times;
\item The user does not need to create the new public key ahead of
  time. Instead, he can create it when he has lost the former one,
  decreasing the likelihood of losing the associated secret key also.
\end{itemize}
